### 2023-04-19 paper.tex
made suppl figs non-floating

\usepackage[a4paper,hmargin=1.5cm,vmargin=2cm]{geometry}
\setlength{\columnsep}{0.7cm}
%\usepackage{microtype} % nice typesetting  % doesn't work for me :-( -S
\usepackage{amsmath}
\usepackage{graphicx}

@@

S.\ A.\ and L.\ P.\ M.\ K.\ acknowledge funding by the Klaus Tschira Foundation.
L.\ P.\ M.\ K., L.\ K., S.\ C.\ and A.\ M.-V.\ acknowledge funding from the European Commission via ERC grant 771376.
We thank Alexey Uvarovskii for code refactoring and helpful suggestions on the source code.

@@

\newpage
\section{Supplementary Figures}

@@

\begin{figure*}
    \begin{center}
        \includegraphics[width=0.8\columnwidth]{figures/SFig_benchmark.png}
    \end{center}
    \caption{\small \textbf{Benchmark of our methods on single-cell methylomes of neural subtypes of the murine frontal cortex}.\\
    Our methods were benchmarked on single-cell methylomes from \citet{luo2017single} as described in Fig.~\ref{fig:score}.
    }
    \label{fig:score_luo}
\end{figure*}

\begin{figure*}
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/SFig_parameter_sweep.png}
    \end{center}
    \caption{\small \textbf{Effect of VMR detection parameters on separation of cell types}.\\
    \textbf{(A-B)} Mean neighbor scores obtained after analyzing single-cell methylomes from \citet{kremer_scnmt} (\textbf{A}) or \citet{luo2017single} (\textbf{B}) with our proposed methods.
    VMRs were detected with \texttt{scbs scan} using various sliding window bandwidths or variance thresholds, and on sub-samples of the full data sets.
    }
    \label{fig:sweep}
\end{figure*}

>>>>

\usepackage[a4paper,hmargin=1.5cm,vmargin=2cm]{geometry}
\setlength{\columnsep}{0.7cm}
%\usepackage{microtype} % nice typesetting  % doesn't work for me :-( -S
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{caption}

@@

SA and LPMK acknowledge funding by the Klaus Tschira Foundation (project 00.022.2019).
LPMK, LK, SC, and AMV acknowledge funding from the European Commission via ERC grant 771376.
We thank Alexey Uvarovskii for code refactoring and helpful suggestions on the source code.
\bigskip

@@

\onecolumn 
\newpage
\section{Supplementary Figures}
\bigskip

@@

\noindent%
\begin{minipage}{\linewidth}
	\begin{center}
	    \includegraphics[width=0.6\textwidth]{figures/SFig_benchmark.png}
	\end{center}
	\captionof{figure}{\small \textbf{Benchmark of our methods on single-cell methylomes of neural subtypes of the murine frontal cortex}.\\
	Our methods were benchmarked on single-cell methylomes from \citet{luo2017single} as described in Fig.~\ref{fig:score}. 
	}
	\label{fig:score_luo}
\end{minipage}
\bigskip

\noindent%
\begin{minipage}{\linewidth}
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/SFig_parameter_sweep.png}
    \end{center}
    \captionof{figure}{\small \textbf{Effect of VMR detection parameters on separation of cell types}.\\
    \textbf{(A-B)} Mean neighbor scores obtained after analyzing single-cell methylomes from \citet{kremer_scnmt} (\textbf{A}) or \citet{luo2017single} (\textbf{B}) with our proposed methods.
    VMRs were detected with \texttt{scbs scan} using various sliding window bandwidths or variance thresholds, and on sub-samples of the full data sets.
    }
    \label{fig:sweep}
\end{minipage}
